---
title: "Getting started with AndyWebsite"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AndyWebsite)
```

## How to launch the dashboard

You can launch the Shiny app by running the following command in your R console:

```{r launch app, eval=FALSE}
launch_app()
```

This opens the HAI Dashboard – German PPS 2011 with:

Cases (interactive): total cases by infection type, with rate per 1,000 patients on hover.

Length of Infection: distribution (days) for a chosen infection type.

About & How to Read: glossary + interpretation notes.

## Data used in the app

The app uses objects provided by BHAI:

num_survey_patients: total number of patients surveyed in the PPS.

population: national population (2011).

length_of_stay: mean hospital length of stay (days).

num_hai_patients: named vector of case counts by infection type (HAP, SSI, BSI, UTI, CDI).

loi_pps: list of vectors with length of infection (days) per type.

Note: These are prevalence-oriented summaries from a point-prevalence survey (PPS), not incident cases over time.

## How to read the app’s outputs

### Field glossary

Infection - HAI type: HAP (Hospital-Acquired Pneumonia), SSI (Surgical Site Infection), BSI (Bloodstream Infection), UTI (Urinary Tract Infection), CDI (Clostridioides difficile Infection).

Cases: The number of surveyed patients identified with that infection type (num_hai_patients).

Rate per 1,000 patients: Standardized rate 1000 \* cases / num_survey_patients, enabling fair comparisons.

Days: Infection duration (in days) for a patient. Values come from loi_pps[[type]] (statistical draws used for burden estimation).

Count: number of infections that lasted exactly that number of days.

### Interpretation

Cases (interactive) Taller bars = more prevalent infection types in the PPS sample. The hover tooltip shows the rate per 1,000 patients to standardise across groups.

Length of Infection The histogram shows how long infections lasted. Peaks at low days ⇒ many infections resolved quickly; a long right tail which means a subset had prolonged duration.

Read prevalence (how common) together with duration (how long) to reason about potential burden.
